Computing solution space properties by generic programming tensor networks \thanks{\funding{...}}

### 2022-03-21 paper/paper.tex
Updates from Overleaf

\begin{figure}[t] 
    \centering
    \includegraphics[width=\textwidth, trim={0cm 1cm 0cm 0cm}, clip]{figures/lattices.pdf}
    \caption{The types of graphs used in the case study in section \ref{sec:entropy}.
    The lattice dimensions are $L\times L$. (a) square lattice graphs. (b) square lattice graphs with a filling factor $p=0.8$.
    (c) King's graphs. (d) King's graphs with a filling factor $p=0.8$.}
    \label{fig:lattices}
\end{figure}

@@

    \includegraphics[width=\textwidth, trim={0.5cm 0cm 0.5cm 1cm}, clip]{figures/fig6.pdf}

>>>>

\begin{figure}[t] 
    \centering
    \includegraphics[width=\textwidth, trim={0cm 1cm 0cm 1cm}, clip]{figures/lattices.pdf}
    \caption{The types of graphs used in the case study in section \ref{sec:entropy}.
    The lattice dimensions are $L\times L$. (a) square lattice graphs. (b) square lattice graphs with a filling factor $p=0.8$.
    (c) King's graphs. (d) King's graphs with a filling factor $p=0.8$.}
    \label{fig:lattices}
\end{figure}

@@

    \includegraphics[width=\textwidth, trim={0.0cm 0cm 0.0cm 0cm}, clip]{figures/fig6.pdf}
